Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-16 paper/main.tex
write short introductory note for applications section

>>>>

In this section we apply the previously developed methods to the problem of parameter estimation
of our model.
We cover 3 distinct cases with increasing level of complexity.
In the first study, we utilize results previously obtained by \cite{Amir2014,Amir2014_2} who
investigated elastic deformations of \textit{E.Coli} that are partially trapped within a narrow
tube and subject to a force resulting from a fluidic flow.
This setup does not involve any cell-cell interactions but specifically requires a flexible rod.
It is therefore well suited as a starting point to assess the usefulness of our methods and the
ability of our model to describe these results.\\
The last two cases consider time-series of microscopic images containing multiple cells (see
subsection~\ref{section:application-2}) which will be used to perform a parameter estimation of our
full mechanical model.
The approach is split into a first part which considers a time interval that does not contain any
division events and a second part which extends the initially chosen interval to include division
events.
In the first part, we utilize the direct comparison algorithm while the latter requires usage of the
imaging-based comparison algorithm.
